%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumitem}
\usepackage[none]{hyphenat}

\usepackage{lineno}
\linenumbers

\setlength{\parskip}{4pt}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nicholas Chieppa} % Your name
\address{7 Elmay Place \\ East Northport NY 11731} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{631-388-0975 \\ nicholaschieppa@gmail.com} % Your phone number and email
\avaibility{Available to start in June 2021}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}
Diligent computer science student looking for an organization where I can apply my Software Engineering skills to
 meaningfully advance a team objective and meet company needs. 
\end{rSection}

\begin{rSection}{Education}

{\bf Rochester Institute of Technology, Rochester, NY} \hfill {\em Expected, May 2021} 
\\ Bachelor of Science in Computer Science
\\ Minor in Mathematics
\\ GPA: 3.56 / 4.00
\\ Coursework Includes:  Data Management, Parallel and Distributed Systems, Computer Graphics, Artificial Intelligence, Software Engineering, and Web.

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
\end{rSection}

%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience} 
Software Engineering Intern - Homesite Insurance \hfill {\em June to December 2020}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
    \item Worked with a team of software engineers to develop and support the insurance e-Commerce platform at
    Homesite.
    \item Added application performance metrics to existing projects; integrated metrics with Datadog.
    \item Collaborated with experienced cross-disciplinary Homesite team members to analyze, design and develop innovative product features.
\end{itemize}
\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Stream-Notifier (Java)} \hfill {\em Personal Project}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
    \item Developed a bot that can respond to visual events that occur on a twitch.tv live-stream. 
    \item Designed a simple algorithm to create a template image which could be compared against sections of a live captured image.
    \item Implemented an android interface that can receive notifications of events that happen on stream and display actions a user can take.
\end{itemize}

{\bf Database Management System (Java)} \hfill {\em Team Semester Project}
\setlist{nolistsep}
\begin{itemize}[noitemsep]
    \item Created a database system from scratch; implementing I/O, conditional searches, and projection on general datasets.
    \item Made use of software buffers to reduce the amount of time spent writing to disk, improving the databases speed. 
    \item Coordinated meetings with team members, scheduled rooms, and slack meetings.
\end{itemize}

% {\bf Web-Checkers (Java)} \hfill {\em Team Semester Project}
% \setlist{nolistsep}
% \begin{itemize}[noitemsep]
%     \item Coordinated with a team to develop an online checkers game.
%     \item Used agile design principles to plan and elaborate on development goals.
%     \item Integrated GitHub's branching feature into the teams workflow in order to create and test each feature independently.
% \end{itemize}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Experienced Programming Languages: \ & Java, C, Python\\
Some Programming Experience With: & OpenGL, C++, JavaScript (HTML), Junit, SQL\\
Software \& Tools: & GitHub, Trello, Vim, Visual Studio, IntelliJ
\end{tabular}

\end{rSection}


%	Academic Achievements
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
Dean's List at RIT  \hfill { \em Fall 2017 - Present}
\end{rSection}


%	OTHER WORK EXPERIENCE
%----------------------------------------------------------------------------------------

% \begin{rSection}{Other Work Experience} 
% Part-Time Cashier - GAP  \hfill {\em May to August 2019} \\
% Part-Time Cashier - Sears Holding Corporation  \hfill {\em June to August 2017} \\
% \end{rSection}

\end{document}